Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-29 04_Prep_data.Rmd
Spellcheck
Prep AUDPC data and inspect on plot

controlY <-
   mean(dat1[dat1$fungicide == "control", "grain_yield.t.ha."])

dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain / controlY
dat1[dat1$fungicide == "control", c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1

@@

## Reduce dataset to required variables  
Lets tidy up the dataset into a data frame of only the variables which are required for the analysis.

@@

>>>>

controlY <-
   mean(dat1[dat1$fungicide_ai == "control", "grain_yield.t.ha."])

dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain / controlY
dat1[dat1$fungicide_ai == "control", c("yield_gain", "prop_YG")] <- c(NA,NA)
PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1

@@

## Reduce data set to required variables  
Lets tidy up the data set into a data frame of only the variables which are required for the analysis.

@@

```{r Yield_vs_AUDPC}

slimmer_PM_dat %>%
   filter(AUDPC_m <=280)%>%
#   filter(fungicide_ai == "control")%>%
   ggplot(aes(x = grain_yield.t.ha, y = AUDPC_m))+
   geom_point()

summary(lm(grain_yield.t.ha ~ AUDPC_m, data = subset(slimmer_PM_dat, AUDPC_m <= 280)))

plot(grain_yield.t.ha. ~ AUDPC_m,data = subset(PM_MB_means, AUDPC_m <= 280) )
abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = subset(PM_MB_means, AUDPC_m <= 280)))

for(i in unique(PM_MB_means$trial_ref)){

   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]
   if(any(is.na(dat1$grain_yield.t.ha.))){next}
   if(any(is.na(dat1$AUDPC_m))){next}

plot(grain_yield.t.ha. ~ AUDPC_m, data = dat1, main = paste(dat1$location[1],(dat1$year[1])),ylim = c(0,2.5) , xlim = c(0,300))
abline(lm(grain_yield.t.ha. ~ AUDPC_m, data = dat1))
points(grain_yield.t.ha. ~ AUDPC_m, data = dat1[dat1$fungicide_ai == "control",], col = "red")
